---
title: "accuracy_calculation"
output: html_document
date: "2024-09-24"
---

```{r setup, include=FALSE}
# surpress warnings
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

## Accuracy calculations for plotting

In this document we are performing the preparatory analysis calculations to plot the figures for the RIDER paper.
We decided to do these calculations in a separate document, as otherwise the plotting script would be too crowded.

```{r environment preparation,include=FALSE}
#clean environment
rm(list = ls()) 

#Libraries
library(plyr) #Ssplitting, applying and combining Data
library(dplyr) # for general data manipulation
library(ggplot2) # for visualizations
library(purrr)#working with functions and vectors
library(stringr)#working with strings
library(purrr)# for plotting
library(tidyverse)#different aspects of data processing
library(reshape)# for general data manipulation
library(scico)#colour palettes fpr plotting
library("readxl")
library(circular)
library(Rmisc)
library(ggpubr)# for plotting
library(rstatix)#for stats
library(viridis)# for nice plotting colors
library(data.table)
library(BayesFactor)#for performing a Bayesian t-test
library(cowplot)#for plotting
library(ggstatsplot)
library(formatR)
library(PupillometryR)
library(sm)
library(hrbrthemes)#nice plotting
library(viridis)#nice plotting
library(gridExtra)
library(plotly)# intersczive plotting
 library(ggpubr)
`%notin%` <- Negate(`%in%`)
```
Here, I am loading the dataframes that contain the raw participant data, which you can find in the respective GIN repository of this project.
Important, please note: RIDER 1 equals RIDER1 (continous orientation test); RIDER 2 that is indicated to be the second experiment in this script holds the data for the third experiment in the manuscript. RIDER V3 is therefore RIDER2 in this script. This is important to know to aviod confusion.
```{r data, echo=FALSE}
# RIDER1 data
data_WM <- read.csv("/Users/born/Documents/Upside_down_task/client/public/raw_data/WM_data.csv",na.strings=c("","NA"))
data_LTM <- read.csv("/Users/born/Documents/Upside_down_task/client/public/raw_data/LTM_data.csv",na.strings=c("","NA"))

# RIDER2a data (manuscript: RIDER3)
data_WM_V2 <- read.csv("/Users/born/Documents/Upside_down_task/client/public/WM_data_V2.csv",na.strings=c("","NA"))
data_LTM_V2 <- read.csv("/Users/born/Documents/Upside_down_task/client/public/LTM_data_V2.csv",na.strings=c("","NA"))

# data second round data collection RIDER 2a
data_WM_V2n <- read.csv("/Users/born/Documents/Upside_down_task/client/public/WM_data_V2_nacherhebung.csv",na.strings=c("","NA"))
data_LTM_V2n <- read.csv("/Users/born/Documents/Upside_down_task/client/public/LTM_data_V2_nacherhebung.csv",na.strings=c("","NA"))

# combine pilot and exp. files for RIDER 2a, to increase participant number
# Add ".2" to each participant name in the pilot df to make visibly who is the pilot participant
data_WM_V2n$participant <- paste0(data_WM_V2n$participant, ".2")
data_LTM_V2n$participant <- paste0(data_LTM_V2n$participant, ".2")

# Delete specified columns
data_WM_V2n <- subset(data_WM_V2n, select = -c(participant.1, trial_type.1, new_column))
data_LTM_V2n <- subset(data_LTM_V2n, select = -c(new_column))

data_WM_V2 <- rbind(data_WM_V2,data_WM_V2n)
data_LTM_V2 <- rbind(data_LTM_V2,data_LTM_V2n)

# RIDER3 data (manuscript: RIDER2)
data_WM_V3 <- read.csv("/Users/born/Documents/RIDER3/client/public/data/WM_data_RIDER_3.csv",na.strings=c("","NA"))
data_LTM_V3 <- read.csv("/Users/born/Documents/RIDER3/client/public/data/LTM_data_RIDER_3.csv",na.strings=c("","NA"))

data_LTM_V3 <- data_LTM_V3[!(as.character(data_LTM_V3$timeout_ltm) == "1"), ]
```
 
```{r accuracy calculation, echo=FALSE}
# function that calculates accuracy for all experiments

angdiff <- function(alpha_deg, beta_deg) {
  #The function assumes that the input angles alpha and beta are in radians.So, you will have to convert them to radians first:
  alpha_rad <- alpha_deg * pi / 180
  beta_rad <- beta_deg * pi / 180
  # Then, you calculate the difference in angles
  delta_rad <- alpha_rad - beta_rad
  # If your input angles alpha and beta are larger than 360°, the mod() function will correctly wrap them to the range of [-180,180] degrees interval.
  delta_rad <- (delta_rad + pi) %% (2*pi) - pi
  delta_deg <- delta_rad * 180 / pi
  #the function outputs both the angular difference in degrees and in radians
  return(list(delta_rad = delta_rad, delta_deg = delta_deg))
}

```
 
RIDER1
```{r RIDER1, echo=FALSE}

# Group the data by participant and remove the first 6 trials for each participant (those where training trials)
data_WM <- data_WM %>%
  group_by(participant) %>%
  slice(7:n()) %>%
  ungroup()

#calculating the correct fixed orientations for the 2-item trials:
#depending on whether the stimulus was presented in image 1 or image 2
data_WM$startOri1 <- as.character(data_WM$startOri1)

data_WM <- data_WM %>%
  rowwise() %>%
  mutate(fixedOri_t1 = ifelse((test1 == image1), startOri1,ifelse((test1 ==  image2),startOri2,NA)))


data_WM <- data_WM %>%
  rowwise() %>%
  mutate(fixedOri_t2 = ifelse((test2 == image1), startOri1,ifelse((test2 ==  image2),startOri2,NA)))

# calculate remainder of this_ori variable to adjust for cases that are beyond 360 degrees
data_WM <- data_WM %>% mutate(ori_t1_corrected = this_ori_t1 %% 360)#Modulus (Remainder from division)
data_WM <- data_WM %>% mutate(ori_t2_corrected = this_ori_t2 %% 360)#Modulus (Remainder from division)

data_WM$fixedOri_t1 <- as.numeric(data_WM$fixedOri_t1)
data_WM$fixedOri_t2 <- as.numeric(data_WM$fixedOri_t2)

# absolute error (radians)
data_WM$accuracy_t1_rad <- apply(data_WM[, c("this_ori_t1", "fixedOri_t1")], 1, function(x) abs(angdiff(x[1], x[2])$delta_rad))
data_WM$accuracy_t2_rad <- apply(data_WM[, c("this_ori_t2", "fixedOri_t2")], 1, function(x) abs(angdiff(x[1], x[2])$delta_rad))


# absolut accuracy in degrees
data_WM$accuracy_t1 <- abs(apply(data_WM[,c("this_ori_t1", "fixedOri_t1")], 1, function(x) angdiff(x[1], x[2])$delta_deg))
data_WM$accuracy_t2 <- abs(apply(data_WM[,c("this_ori_t2", "fixedOri_t2")], 1, function(x) angdiff(x[1], x[2])$delta_deg))

# accuracy signed (degrees)
data_WM$accuracy_t1_signed_deg <- apply(data_WM[, c("this_ori_t1", "fixedOri_t1")], 1, function(x) angdiff(x[1], x[2])$delta_deg)
data_WM$accuracy_t2_signed_deg <- apply(data_WM[, c("this_ori_t2", "fixedOri_t2")], 1, function(x) angdiff(x[1], x[2])$delta_deg)

# pivot longer (here for degrees, as I am plotting in degrees)
data_WM_long<- data_WM %>% pivot_longer(cols=c('accuracy_t1','accuracy_t2'),names_to='attention_condition',values_to='accuracy') 

# accuracy and trial types for LTM task 
data_LTM<-data_LTM[!(data_LTM$participant=='15'),]

data_LTM <- rbind.fill(data_LTM,data_WM[c("test1", "test2","participant","image1","image2")])

# defining the menemonic distance conditions

# defining the simple trial types (as broader experimental conditions)
data_LTM <- data_LTM %>%
  group_by(participant)%>%
  mutate(trial_type = case_when(ltm_image %in% test1 & ltm_trial == 'baseline' ~ "Baseline",
                                 ltm_image %in%  test1  ~   "Test 1",
                                 ltm_image %in%  test2  ~   "Test 2",
                                 ltm_image %notin% test1 & ltm_image %notin% test2 ~ "Never tested"))

data_LTM <- data_LTM %>%
  group_by(participant)%>%
  mutate(image_presentation = case_when(ltm_trial == 'baseline' ~ "Baseline",
                                 ltm_image %in%  test1 & ltm_image %in% image1  ~   "Img1-Test1",
                                 ltm_image %in%  test1 & ltm_image %in% image2  ~   "Img2-Test1",
                                 ltm_image %in%  test2 & ltm_image %in% image1  ~   "Img1-Test2",
                                 ltm_image %in%  test2 & ltm_image %in% image2  ~   "Img2-Test2",
                                 ltm_image %notin% test1 & ltm_image %notin% test2 & ltm_image %in% image1 ~ "Img1-NT",
                                 ltm_image %notin% test1 & ltm_image %notin% test2 & ltm_image %in% image2 ~ "Img2-NT"))

# calculate ltm accuracy
data_LTM <- data_LTM %>% mutate(ori_ltm = this_ori_ltm %% 360)#Modulus (Remainder from division)

# calculating accuracy for LTM test
data_LTM <- data_LTM %>% 
  rowwise() %>%
  mutate(min_angle_ltm = abs(ori_ltm -fixedOri_ltm))%>%
  mutate(max_angle_ltm = 360-abs(ori_ltm -fixedOri_ltm))

data_LTM <- transform(data_LTM, accuracy_ltm = pmin(min_angle_ltm, max_angle_ltm))#angular difference

data_LTM <- data_LTM %>% 
  rowwise() %>%
  mutate(angle_ltm = this_ori_ltm -fixedOri_ltm)

#remove extra WM rows again
data_LTM <- data_LTM[rowSums(is.na(data_LTM)) == 0|rowSums(is.na(data_LTM)) == 1| rowSums(is.na(data_LTM)) == 2|rowSums(is.na(data_LTM)) == 3|rowSums(is.na(data_LTM)) == 4,]

# absolute error radians
data_LTM$accuracy_ltm_rad <- apply(data_LTM[, c("this_ori_ltm", "fixedOri_ltm")], 1, function(x) abs(angdiff(x[1], x[2])$delta_rad))


# WM trial_type

# simple retrieval trial types
data_WM_long <- data_WM_long  %>% 
  mutate(trial_type_new = case_when(
    baselinePresent  == 1 ~ "Baseline",
    trial_type !="baseline" & attention_condition == "accuracy_t1"  ~ "Test 1",
    trial_type !="baseline" & attention_condition == "accuracy_t2" ~ "Test 2"))

# image effect
data_WM_long <- data_WM_long  %>% 
  mutate(image_presentation = case_when(
    baselinePresent  == 1 ~ "Baseline",
    image1 == test1 & attention_condition == "accuracy_t1"  ~ "Img1-Test1",
    image1 == test2 & attention_condition == "accuracy_t2" ~ "Img1-Test2",
    image2 == test2 & attention_condition == "accuracy_t2" ~ "Img2-Test2",
    image2 == test1 & attention_condition == "accuracy_t1" ~ "Img2-Test1"))

# drop rows where we have no data
data_WM_long <-data_WM_long %>% drop_na(accuracy)

# one participant is excluded due to low performance (see detailed RIDER1 script for wilcoxon test)
data_WM_long<-data_WM_long[!(data_WM_long$participant=='15'),]

# remove trials where reaction times are extremely long (> 15s)

# extract adjust_keys_t2_numeric from adjust_keys_t2.rt
data_WM_long$adjust_keys_t2_numeric <- apply(data_WM_long, 1, function(x) as.numeric(gsub("\\[|\\]", "", x["adjust_keys_t2.rt"])))

# extract adjust_keys_t1_numeric from adjust_keys_t1.rt
data_WM_long$adjust_keys_t1_numeric <- apply(data_WM_long, 1, function(x) as.numeric(gsub("\\[|\\]", "", x["adjust_keys_t1.rt"])))


data_WM$adjust_keys_t2_numeric <- apply(data_WM, 1, function(x) as.numeric(gsub("\\[|\\]", "", x["adjust_keys_t2.rt"])))

# extract adjust_keys_t1_numeric from adjust_keys_t1.rt
data_WM$adjust_keys_t1_numeric <- apply(data_WM, 1, function(x) as.numeric(gsub("\\[|\\]", "", x["adjust_keys_t1.rt"])))

# create a logical vector for filtering
filter_vec <- ((data_WM_long$adjust_keys_t2_numeric <= 15) | is.na(data_WM_long$adjust_keys_t2_numeric)) & ((data_WM_long$adjust_keys_t1_numeric <= 15) | is.na(data_WM_long$adjust_keys_t1_numeric))

# filter the data
data_WM_long <- data_WM_long[filter_vec,]
```

```{r pruning RIDER1, include=FALSE}

removed_trials <- read.csv("/Users/born/Documents/Upside_down_task/client/public/pruning_removed_trials/removed_trials.csv",na.strings=c("","NA"))
removed_trials2 <- read.csv("/Users/born/Documents/Upside_down_task/client/public/pruning_removed_trials/removed_trials2.csv",na.strings=c("","NA"))
#write.csv(removed_trials,"/Users/born/Documents/Upside_down_task/client/public/removed_trials.csv", row.names = FALSE)
objects <- removed_trials %>%
  group_by(participant,trial_type_new)%>%
  summarise(test1,test2)

objects<- objects %>% pivot_longer(cols=c('test1', 'test2'),names_to='Presentation',values_to='image1') 

objects <- objects %>%
  rowwise()%>%
  mutate(delete = case_when(trial_type_new == "Test 1" & Presentation == "test2"  ~ "delete",
                            trial_type_new == "Test 2" & Presentation == "test1"  ~ "delete",
                            trial_type_new == "Test 1" & Presentation == "test1"  ~ "no_delete",
                            trial_type_new == "Test 2" & Presentation == "test2"  ~ "no_delete",
                            trial_type_new == "Baseline" & Presentation == "test2"  ~ "delete",
                            trial_type_new == "Baseline" & Presentation == "test1"  ~ "no_delete"))

objects<-objects[(objects$delete== "no_delete"),]

# identification of ltm object pool that includes only pruned WM conditions (Test 1 and Test 2 is effected here)
data_LTM <- rbind.fill(data_LTM,objects[c("participant", "image1")])

data_LTM <- data_LTM %>%
  group_by(participant)%>%
  mutate(matching = case_when(ltm_image %in% image1  ~ "Match",
                              ltm_image %notin%  image1  ~   "NO_Match"))


data_LTM <- data_LTM[rowSums(is.na(data_LTM)) == 1|rowSums(is.na(data_LTM)) == 2|rowSums(is.na(data_LTM)) == 3|rowSums(is.na(data_LTM)) == 4,]

# delete all matching trials in ltm dataframe
data_LTM_pruned<-data_LTM[!(data_LTM$matching=="Match"),]

data_LTM$pruned <- "NO"
data_LTM_pruned$pruned <-"YES"

## remove the trials with long rts > 15s 
data_LTM_pruned$adjust_keys_LTM.rt_numeric <- apply(data_LTM_pruned, 1, function(x) as.numeric(gsub("\\[|\\]", "", x["adjust_keys_LTM.rt"])))

# create a logical vector for filtering
filter_vec <- (data_LTM_pruned$adjust_keys_LTM.rt_numeric <= 15)

# filter the data
data_LTM_pruned <- data_LTM_pruned[filter_vec,]


LTM <- rbind(data_LTM,data_LTM_pruned)
```


```{r WM Bias RIDER1, include=FALSE}
summary_stats_LTM_P <- summarySE(LTM, measurevar = "accuracy_ltm", groupvars = c("trial_type","participant","pruned"),na.rm = T)

summary_stats_participant_pruned <- summarySE(data_LTM_pruned, measurevar = "accuracy_ltm", groupvars = c("trial_type","participant"),na.rm = T)

summary_study_level_LTM_g <- summarySE(summary_stats_LTM_P, measurevar = "accuracy_ltm", groupvars = c("trial_type","pruned"),na.rm = T)

data_LTM$adjust_keys_LTM.rt_numeric <- apply(data_LTM, 1, function(x) as.numeric(gsub("\\[|\\]", "", x["adjust_keys_LTM.rt"])))

# create a logical vector for filtering
filter_vec <- (data_LTM$adjust_keys_LTM.rt_numeric <= 15)

# filter the data
data_LTM <- data_LTM[filter_vec,]


test_2_data2 <- subset(data_LTM, trial_type == "Test 2", select = c("participant","ltm_image","this_ori_ltm","ori_ltm"))
test_2_data_WM2 <- subset(data_WM_long, trial_type_new == "Test 2", select = c("participant","test1","test2","ori_t1_corrected","ori_t2_corrected"))
test_2_data2 <- rbind.fill(test_2_data2,test_2_data_WM2[c("participant","test1","test2","ori_t1_corrected","ori_t2_corrected")])

test2_trials2 <-split(test_2_data2,test_2_data2$participant)

for(df in 1:length(test2_trials2)) {
  test2_trials2[[df]]$alternative_memory2 <- sapply(test2_trials2[[df]]$ltm_image,function(x) test2_trials2[[df]]$ori_t2_corrected[grep(x,test2_trials2[[df]]$test2)[1]])
}

test_2_data2 <- rbindlist(test2_trials2)

test_2_data2 <- test_2_data2 %>% 
  rowwise() %>%
  mutate(min_angle_ltm = abs(ori_ltm - alternative_memory2))%>%
  mutate(max_angle_ltm = 360-abs(ori_ltm - alternative_memory2))

test_2_data2 <- transform(test_2_data2, accuracy_ltm = pmin(min_angle_ltm, max_angle_ltm))#angular difference

# extract data for WM bias in baseline over participants

test_baseline_data2 <- subset(data_LTM, trial_type == "Baseline", select = c("participant","ltm_image","this_ori_ltm","ori_ltm"))
data_baseline2 <- subset(data_WM_long, trial_type_new == "Baseline", select = c("participant","test1","test2","ori_t1_corrected","ori_t2_corrected"))
test_baseline_data2 <- rbind.fill(test_baseline_data2,data_baseline2[c("participant","test1","test2","ori_t1_corrected","ori_t2_corrected")])

baseline_trials2 <-split(test_baseline_data2,test_baseline_data2$participant)

for(df in 1:length(baseline_trials2)) {
  baseline_trials2[[df]]$alternative_memory2 <- sapply(baseline_trials2[[df]]$ltm_image,function(x) baseline_trials2[[df]]$ori_t1_corrected[grep(x,baseline_trials2[[df]]$test1)[1]])
}

baseline_trials2 <- rbindlist(baseline_trials2)

baseline_trials2 <- baseline_trials2 %>% 
  rowwise() %>%
  mutate(min_angle_ltm = abs(ori_ltm - alternative_memory2))%>%
  mutate(max_angle_ltm = 360-abs(ori_ltm - alternative_memory2))

baseline_trials2 <- transform(baseline_trials2, accuracy_ltm = pmin(min_angle_ltm, max_angle_ltm))#angular difference

# extract data for WM bias in Test 1 over participants

test_1_data2 <- subset(data_LTM, trial_type == "Test 1", select = c("participant","ltm_image","this_ori_ltm","ori_ltm"))
test_1_data_WM2 <- subset(data_WM_long, trial_type_new == "Test 1", select = c("participant","test1","test2","ori_t1_corrected","ori_t2_corrected"))
test_1_data2 <- rbind.fill(test_1_data2,test_1_data_WM2[c("participant","test1","test2","ori_t1_corrected","ori_t2_corrected")])

test1_trials2 <-split(test_1_data2,test_1_data2$participant)

for(df in 1:length(test1_trials2)) {
  test1_trials2[[df]]$alternative_memory2 <- sapply(test1_trials2[[df]]$ltm_image,function(x) test1_trials2[[df]]$ori_t1_corrected[grep(x,test1_trials2[[df]]$test1)[1]])
}

test_1_data2 <- rbindlist(test1_trials2)


test_1_data2 <- test_1_data2 %>% 
  rowwise() %>%
  mutate(min_angle_ltm = abs(ori_ltm - alternative_memory2))%>%
  mutate(max_angle_ltm = 360-abs(ori_ltm - alternative_memory2))

test_1_data2 <- transform(test_1_data2, accuracy_ltm = pmin(min_angle_ltm, max_angle_ltm))#angular difference

# add trials type 
test_1_data2$trial_type <- "Test 1"
test_2_data2$trial_type <- "Test 2"
baseline_trials2$trial_type <- "Baseline"


alternative_ltm2 <- rbind(test_1_data2,test_2_data2,baseline_trials2)

summary_stats_participant_WB <- summarySE(alternative_ltm2, measurevar = "accuracy_ltm", groupvars = c("trial_type","participant"),na.rm = T)
summary_study_level_WB <- summarySE(summary_stats_participant_WB, measurevar = "accuracy_ltm", groupvars = c("trial_type"),na.rm = T)

```


 RIDER1 summary dataframes for plotting
 1) Participant means (here not printed)
 2) Sample means per condition (printed for an overview)
```{r RIDER1 summary, echo=FALSE}
### Working memory summary
# Here I am calculating the summaries for participants and the full sample to prepare the plotting
summary_stats_participant_image_pres <- summarySE(data_WM_long, measurevar = "accuracy", groupvars = c("image_presentation","participant"),na.rm = T)
summary_study_level_image_pres <- summarySE(summary_stats_participant_image_pres, measurevar = "accuracy", groupvars = c("image_presentation"),na.rm = T)
summary_study_level_image_pres$participant <- 1

print("Sample menas WM")
summary_study_level_image_pres

# Convert 'participant' to a factor explicitly
summary_stats_participant_image_pres$participant <- factor(summary_stats_participant_image_pres$participant)
summary_study_level_image_pres$participant <- factor(summary_study_level_image_pres$participant)
# also in preparation for plotting
level_order12 = c('Baseline','Img1-Test1','Img2-Test1','Img1-Test2','Img2-Test2')


#### Long-term Memory
print("Sample menas LTM")

# Image effect subplot
summary_stats_participant_LTM_ip <- summarySE(data_LTM, measurevar = "accuracy_ltm", groupvars = c("image_presentation","participant"),na.rm = T)
summary_study_level_ip <- summarySE(summary_stats_participant_LTM_ip, measurevar = "accuracy_ltm", groupvars = c("image_presentation"),na.rm = T)

summary_study_level_ip$participant <- 1

summary_stats_participant_LTM_ip$participant <- factor(summary_stats_participant_LTM_ip$participant)
summary_study_level_ip$participant <- factor(summary_study_level_ip$participant)
# also only preparation for plotting
level_order2 <- c('Baseline','Img1-Test1', 'Img2-Test1', 'Img1-Test2','Img2-Test2','Img1-NT','Img2-NT')

summary_study_level_ip
```

```{r RIDER1 LTMcomparison pruned, WM_report, WM_sample, echo = FALSE,out.width="130%", fig.cap="<br><br>**Figure** **3**: shows a comparison of pruned, WM_report, WM_sample performance "}

summary_stats_participant_LTM <- summarySE(data_LTM, measurevar = "accuracy_ltm", groupvars = c("trial_type","participant"),na.rm = T)
mean_performance_LTM <- summarySE(data_LTM, measurevar = "accuracy_ltm", groupvars = c("participant"),na.rm = T)

summary_study_level_LTM <- summarySE(summary_stats_participant_LTM, measurevar = "accuracy_ltm", groupvars = c("trial_type"),na.rm = T)

summary_study_level_LTM$WM_point <- "WM_sample"
summary_study_level_LTM_g$WM_point <- "pruned"
summary_study_level_WB$WM_point <- "WM_report"
summary_stats_LTM_P$WM_point <- "pruned"



summary_study_level_LTM_g <- summary_study_level_LTM_g %>%
  mutate(WM_point = ifelse(pruned == "YES", "pruned", "WM_sample"))

combined_data <- bind_rows(summary_study_level_LTM_g, summary_study_level_WB)


# Convert WM_point to a factor with custom levels
#combined_data$WM_point <- factor(combined_data$WM_point, levels = c("WM_report", "WM_sample", "pruned"))
# Set the order of experimental conditions
level_order <- c('One-Sample', 'Test 1', 'Test 2', 'Not Probed')

#change the labels to have better descriptives for the plot
combined_data$WM_point[combined_data$WM_point == 'WM_report'] <- "WM Report"
combined_data$WM_point[combined_data$WM_point == 'WM_sample'] <- "WM Sample"
combined_data$WM_point[combined_data$WM_point == 'pruned'] <- "WM Sample (pruned)"

# change naming if inconsistent
combined_data$trial_type[combined_data$trial_type == 'Baseline'] <- "One-Sample"
combined_data$trial_type[combined_data$trial_type == 'One-item prioritized'] <- "One-Sample"
combined_data$trial_type[combined_data$trial_type == 'Two-item prioritized'] <- "Test 1"
combined_data$trial_type[combined_data$trial_type == 'Two-item deprioritized'] <- "Test 2"
combined_data$trial_type[combined_data$trial_type == 'Never tested'] <- "Not Probed"

custom_colors <- c(
  "WM Sample" = "#FF9999",
  "WM Sample (pruned)" = "#DDA0DD",
  "WM Report" = "#FFD709"

)

# Define custom linetypes
custom_linetypes <- c("WM Report" = "solid", "WM Sample" = "dashed", "WM Sample (pruned)" = "solid")

combined_data_filtered <- combined_data %>%
  filter(trial_type != "Not Probed")

level_order9 <- c('One-Sample','Test 1', 'Test 2')

dodge_width <- 0.75

combined_data_filtered <- combined_data_filtered %>%
  filter(trial_type != "Not Probed")


# Define the desired legend order
desired_order <- c("WM Sample (pruned)","WM Sample","WM Report")


# Print the plot
print("Comaprison pruned/WM report/ WM sample")
combined_data_filtered

```

 RIDER2 (manuscript RIDER3)
```{r RIDER2, echo=FALSE}
# Group the data by participant and remove the first 6 trials for each participant
data_WM_V2 <- data_WM_V2 %>%
  group_by(participant) %>%
  slice(7:n()) %>%
  ungroup()

#calculating the correct fixed orientations for the 2-item trials:
#depending on whether the stimulus was presented in image 1 or image 2
data_WM_V2$startOri1 <- as.character(data_WM_V2$startOri1)

data_WM_V2 <- data_WM_V2 %>%
  rowwise() %>%
  mutate(fixedOri_t1 = ifelse((test1 == image1), startOri1,ifelse((test1 ==  image2),startOri2,NA)))

data_WM_V2 <- data_WM_V2 %>%
  rowwise() %>%
  mutate(fixedOri_t2 = ifelse((test2 == image1), startOri1,ifelse((test2 ==  image2),startOri2,NA)))

# calculate remainder of this_ori variable to adjust for cases that are beyond 360 degrees
data_WM_V2 <- data_WM_V2 %>% mutate(accuracy_t1 = log_response_t1.corr)#Modulus (Remainder from division)
data_WM_V2 <- data_WM_V2 %>% mutate(accuracy_t2 = log_response_t2.corr)#Modulus (Remainder from division)
# 
# # calculating accuracy for test 1 and test 2
data_WM_V2$accuracy_t1 <- as.numeric(data_WM_V2$accuracy_t1)

data_WM_V2$accuracy_t2 <- as.numeric(data_WM_V2$accuracy_t2)

# I remove the rows in which either for test 1 or test 2 the participant did not answer in time
data_WM_V2<-data_WM_V2[!(data_WM_V2$imgChoice1=='stim/respond_faster.png'),]

data_WM_V2 <- data_WM_V2 %>%
  filter(is.na(imgChoice2) | imgChoice2 != "stim/respond_faster.png")

# pivot longer
data_WM_long_V2<- data_WM_V2 %>% pivot_longer(cols=c('accuracy_t1','accuracy_t2'),names_to='attention_condition',values_to='accuracy')

# extracting numeric reaction times
data_WM_V2$adjust_keys_t1_numeric <- apply(data_WM_V2, 1, function(x) as.numeric(gsub("\\[|\\]", "", x["log_response_t1.rt"])))


data_WM_V2$adjust_keys_t2_numeric <- apply(data_WM_V2, 1, function(x) as.numeric(gsub("\\[|\\]", "", x["log_response_t2.rt"])))

# create separate df for reaction times
data_WM_rt_V2<- data_WM_V2 %>% pivot_longer(cols=c('adjust_keys_t1_numeric','adjust_keys_t2_numeric'),names_to='rt_test',values_to='rt')

# Total number of trials per participant
total_trials_per_participant <- data_WM_V2 %>%
  group_by(participant) %>%
  summarize(total_trials = n())

# Calculate the number of excluded trials per participant
excluded_trials <- data_WM_V2 %>%
  filter(adjust_keys_t1_numeric > 3 | adjust_keys_t2_numeric > 3) %>%
  group_by(participant) %>%
  summarize(excluded_trials_count = n()) %>%
  right_join(total_trials_per_participant, by = "participant") %>%
  mutate(excluded_trials_count = replace_na(excluded_trials_count, 0)) %>%
  mutate(excluded_trials_percent = (excluded_trials_count / total_trials) * 100)

# Print the resulting dataframe to inspect it
print(excluded_trials)

# Calculate the average, minimum, and maximum percentage of excluded trials per participant
excluded_trials_summary <- excluded_trials %>%
  summarize(
    average_excluded_trials_percent = mean(excluded_trials_percent, na.rm = TRUE),
    min_excluded_trials_percent = min(excluded_trials_percent, na.rm = TRUE),
    max_excluded_trials_percent = max(excluded_trials_percent, na.rm = TRUE)
  )


## LTM part
data_LTM_V2 <- rbind.fill(data_LTM_V2,data_WM_V2[c("test1", "test2","participant","image1","image2")])

# defining the menemonic distance conditions


# defining the simple trial types (as broader experimental conditions)
data_LTM_V2 <- data_LTM_V2 %>%
  group_by(participant)%>%
  mutate(trial_type = case_when(ltm_trial == 'baseline' ~ "Baseline",
                                 ltm_image %in%  test1  ~   "Test 1",
                                 ltm_image %in%  test2  ~   "Test 2",
                                 ltm_image %notin% test1 & ltm_image %notin% test2 ~ "Never tested"))


data_LTM_V2 <- data_LTM_V2 %>%
  group_by(participant)%>%
  mutate(image_presentation = case_when(ltm_trial == 'baseline' ~ "Baseline",
                                 ltm_image %in%  test1 & ltm_image %in% image1  ~   "Img1-Test1",
                                 ltm_image %in%  test1 & ltm_image %in% image2  ~   "Img2-Test1",
                                 ltm_image %in%  test2 & ltm_image %in% image1  ~   "Img1-Test2",
                                 ltm_image %in%  test2 & ltm_image %in% image2  ~   "Img2-Test2",
                                 ltm_image %notin% test1 & ltm_image %notin% test2 & ltm_image %in% image1 ~ "Img1-NT",
                                 ltm_image %notin% test1 & ltm_image %notin% test2 & ltm_image %in% image2 ~ "Img2-NT"))



# calculate ltm accuracy
data_LTM_V2 <- data_LTM_V2 %>% mutate(ori_ltm = this_ori_ltm %% 360)#Modulus (Remainder from division)


# calculating accuracy for LTM test
data_LTM_V2 <- data_LTM_V2 %>% 
  rowwise() %>%
  mutate(min_angle_ltm = abs(ori_ltm -fixedOri_ltm))%>%
  mutate(max_angle_ltm = 360-abs(ori_ltm -fixedOri_ltm))

data_LTM_V2 <- transform(data_LTM_V2, accuracy_ltm = pmin(min_angle_ltm, max_angle_ltm))#angular difference

data_LTM_V2 <- data_LTM_V2 %>% 
  rowwise() %>%
  mutate(angle_ltm = this_ori_ltm -fixedOri_ltm)

#remove extra WM rows again
data_LTM_V2 <- data_LTM_V2[rowSums(is.na(data_LTM_V2)) == 0|rowSums(is.na(data_LTM_V2)) == 1| rowSums(is.na(data_LTM_V2)) == 2|rowSums(is.na(data_LTM_V2)) == 3|rowSums(is.na(data_LTM_V2)) == 4,]


# remove participants also from LTM data (same participants as removed for WM) -> performance reasons (statistically on chance level see df = data_WM_mean_acc)
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==39),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==28),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==69),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==62),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==12),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==75),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==71),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==44),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==68),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==29),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==81),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==56),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==77),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==79),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==17),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==46),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==86),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==36),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==60),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==73),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==52),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==78),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==89),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==47),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==43),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==34),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==74),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==97),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==93),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==98),]

data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==1.2),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==3.2),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==5.2),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==13.2),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==17.2),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==26.2),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==31.2),]
data_LTM_V2<-data_LTM_V2[!(data_LTM_V2$participant==42.2),]

# simple retrieval trial types
data_WM_long_V2 <- data_WM_long_V2  %>% 
  mutate(trial_type_new = case_when(
    baselinePresent  == 1 ~ "Baseline",
    trial_type !="baseline" & attention_condition == "accuracy_t1"  ~ "Test 1",
    trial_type !="baseline" & attention_condition == "accuracy_t2" ~ "Test 2"))

# image presentation

data_WM_long_V2 <- data_WM_long_V2  %>% 
  mutate(image_presentation = case_when(
    baselinePresent  == 1 ~ "Baseline",
    image1 == test1 & attention_condition == "accuracy_t1"  ~ "Img1-Test1",
    image1 == test2 & attention_condition == "accuracy_t2" ~ "Img1-Test2",
    image2 == test2 & attention_condition == "accuracy_t2" ~ "Img2-Test2",
    image2 == test1 & attention_condition == "accuracy_t1" ~ "Img2-Test1"))


#drop rows that are NA
data_WM_rt_V2 <-data_WM_rt_V2 %>% drop_na(rt)
data_WM_long_V2 <-data_WM_long_V2 %>% drop_na(accuracy)


# select participants that need to be excluded due to average performance < 0.6
data_WM_mean_acc <- data_WM_long_V2 %>%
  group_by(participant) %>%
  summarize(mean_acc = mean(accuracy))

# remove participant with too low performance average
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==39),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==28),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==69),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==62),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==12),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==75),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==71),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==44),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==68),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==29),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==81),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==56),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==77),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==79),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==17),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==46),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==86),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==36),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==60),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==73),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==52),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==78),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==89),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==47),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==43),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==34),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==74),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==97),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==93),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==98),]

data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==1.2),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==3.2),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==5.2),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==13.2),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==17.2),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==26.2),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==31.2),]
data_WM_long_V2<-data_WM_long_V2[!(data_WM_long_V2$participant==42.2),]

```
RIDER2 summary dataframes for plotting
 1) Participant means (here not printed)
 2) Sample means per condition (printed for an overview)
 
```{r RIDER2 summary, echo=FALSE}

# WM sample presentation plot

summary_stats_participant_image_pres <- summarySE(data_WM_long_V2, measurevar = "accuracy", groupvars = c("image_presentation","participant"),na.rm = T)
summary_study_level_image_pres <- summarySE(summary_stats_participant_image_pres, measurevar = "accuracy", groupvars = c("image_presentation"),na.rm = T)
summary_study_level_image_pres$participant <- 1

# Convert 'participant' to a factor explicitly
summary_stats_participant_image_pres$participant <- factor(summary_stats_participant_image_pres$participant)
summary_study_level_image_pres$participant <- factor(summary_study_level_image_pres$participant)

level_order3 <- c('Baseline','Img1-Test1', 'Img2-Test1','Img1-Test2','Img2-Test2')

print("Sample summary Working memory")
summary_study_level_image_pres


# WM sample effect subplot
summary_stats_participant_LTM_ip <- summarySE(data_LTM_V2, measurevar = "accuracy_ltm", groupvars = c("image_presentation","participant"),na.rm = T)
summary_study_level_ip <- summarySE(summary_stats_participant_LTM_ip, measurevar = "accuracy_ltm", groupvars = c("image_presentation"),na.rm = T)

summary_study_level_ip$participant <- 1

summary_stats_participant_LTM_ip$participant <- factor(summary_stats_participant_LTM_ip$participant)
summary_study_level_ip$participant <- factor(summary_study_level_ip$participant)

level_order2 <- c('Baseline','Img1-Test1', 'Img2-Test1', 'Img1-Test2','Img2-Test2','Img1-NT','Img2-NT')

print("Sample summary Long-term memory")
summary_study_level_ip
```
 RIDER3 (manuscript RIDER2)

```{r RIDER3, echo=FALSE}

data_WM_V3<-data_WM_V3[!(data_WM_V3$participant==63),]
data_LTM_V3<-data_LTM_V3[!(data_LTM_V3$participant==63),]

# Group the data by participant and remove the first 6 trials for each participant
data_WM_V3 <- data_WM_V3 %>%
  group_by(participant) %>%
  slice(7:n()) %>%
  ungroup()

#calculating the correct fixed orientations for the 2-item trials:
#depending on whether the stimulus was presented in image 1 or image 2
data_WM_V3$startOri1 <- as.character(data_WM_V3$startOri1)

# here I determine the orientation the test image was presented in and give it the name fixedOri_t1
data_WM_V3 <- data_WM_V3 %>%
  rowwise() %>%
  mutate(
    fixedOri_t1 = case_when(
      test1 == image1 ~ as.numeric(startOri1),
      test1 == image2 ~ as.numeric(startOri2),
      TRUE ~ NA_real_
    )
  )
# calculate remainder of this_ori variable to adjust for cases that are beyond 360 degrees
data_WM_V3 <- data_WM_V3 %>% mutate(ori_t1_corrected = this_ori_t1 %% 360)#Modulus (Remainder from division)
data_WM_V3$fixedOri_t1 <- as.numeric(data_WM_V3$fixedOri_t1)

# accuracy in radians
data_WM_V3$accuracy_t1_rad <- apply(data_WM_V3[,c("this_ori_t1", "fixedOri_t1")], 1, function(x) angdiff(x[1], x[2])$delta_rad)

# accuracy in degrees
data_WM_V3$accuracy_t1 <- abs(apply(data_WM_V3[,c("this_ori_t1", "fixedOri_t1")], 1, function(x) angdiff(x[1], x[2])$delta_deg))

# calculate ltm accuracy
data_LTM_V3 <- data_LTM_V3 %>% mutate(ori_ltm = this_ori_ltm %% 360)#Modulus (Remainder from division)

# calculating accuracy for LTM test

data_LTM_V3 <- data_LTM_V3 %>% 
  rowwise() %>%
  mutate(min_angle_ltm = abs(ori_ltm -fixedOri_ltm))%>%
  mutate(max_angle_ltm = 360-abs(ori_ltm -fixedOri_ltm))

data_LTM_V3 <- transform(data_LTM_V3, accuracy_ltm = pmin(min_angle_ltm, max_angle_ltm))#angular difference
data_LTM_V3$accuracy_ltm_rad <- (apply(data_LTM_V3[,c("this_ori_ltm", "fixedOri_ltm")], 1, function(x) angdiff(x[1], x[2])$delta_rad))


```


```{r renaming trial types RIDER3, echo=FALSE}
data_WM_V3 <- data_WM_V3  %>% 
  mutate(trial_type_new = case_when(
    trial_type == "attended_1" ~ "attended",
    trial_type == "attended_2" ~ "attended",
    trial_type == "attended_3" ~ "attended",
    trial_type == "attended_4" ~ "attended",
    trial_type == "attended_5" ~ "attended",
    trial_type == "unattended" ~ "unattended"))


data_WM_V3 <- data_WM_V3  %>% 
  mutate(image_effect = case_when(
    trial_type == "attended_1" & image1 %in%  test1 ~ "Image1-attended",
    trial_type == "attended_1" & image2 %in%  test1 ~ "Image2-attended",
    trial_type == "attended_2" & image1 %in%  test1 ~ "Image1-attended",
    trial_type == "attended_2" & image2 %in%  test1 ~ "Image2-attended",
    trial_type == "attended_3" & image1 %in%  test1 ~ "Image1-attended",
    trial_type == "attended_3" & image2 %in%  test1 ~ "Image2-attended",
    trial_type == "attended_4" & image1 %in%  test1 ~ "Image1-attended",
    trial_type == "attended_4" & image2 %in%  test1 ~ "Image2-attended",
    trial_type == "attended_5" & image1 %in%  test1 ~ "Image1-attended",
    trial_type == "attended_5" & image2 %in%  test1 ~ "Image2-attended",
    trial_type == "unattended" & image1 %in%  test1 ~ "Image1-unattended",
    trial_type == "unattended" & image2 %in%  test1 ~ "Image2-unattended",))

data_LTM_V3 <- rbind.fill(data_LTM_V3,data_WM_V3[c("test1","participant","image1","image2")])

data_LTM_V3 <- data_LTM_V3 %>%
  group_by(participant)%>%
  mutate(trial_type = case_when(ltm_trial == 'attended_1' & ltm_image %in%  test1 ~ "attended",
                                 ltm_trial == 'attended_2' & ltm_image %in%  test1 ~ "attended",
                                 ltm_trial == 'attended_3' & ltm_image %in%  test1 ~ "attended",
                                 ltm_trial == 'attended_4' & ltm_image %in%  test1 ~ "attended",
                                 ltm_trial == 'attended_5' & ltm_image %in%  test1 ~ "attended",
                                 ltm_trial == 'unattended' & ltm_image %in%  test1 ~ "unattended",
                                 ltm_trial == 'unattended' & ltm_image %notin% test1  ~ "attended-never tested",
                                 ltm_trial == 'attended_1' & ltm_image %notin% test1  ~ "unattended-never tested",
                                 ltm_trial == 'attended_2' & ltm_image %notin% test1  ~ "unattended-never tested",
                                 ltm_trial == 'attended_3' & ltm_image %notin% test1  ~ "unattended-never tested",
                                 ltm_trial == 'attended_4' & ltm_image %notin% test1  ~ "unattended-never tested",
                                 ltm_trial == 'attended_5' & ltm_image %notin% test1  ~ "unattended-never tested"))

data_LTM_V3 <- data_LTM_V3 %>%
  group_by(participant)%>%
  mutate(attention = case_when(ltm_trial == 'attended_1' & ltm_image %in%  test1 ~ "attended",
                                 ltm_trial == 'attended_2' & ltm_image %in%  test1 ~ "attended",
                                 ltm_trial == 'attended_3' & ltm_image %in%  test1 ~ "attended",
                                 ltm_trial == 'attended_4' & ltm_image %in%  test1 ~ "attended",
                                 ltm_trial == 'attended_5' & ltm_image %in%  test1 ~ "attended",
                                 ltm_trial == 'unattended' & ltm_image %in%  test1 ~ "unattended",
                                 ltm_trial == 'unattended' & ltm_image %notin% test1  ~ "attended",
                                 ltm_trial == 'attended_1' & ltm_image %notin% test1  ~ "unattended",
                                 ltm_trial == 'attended_2' & ltm_image %notin% test1  ~ "unattended",
                                 ltm_trial == 'attended_3' & ltm_image %notin% test1  ~ "unattended",
                                 ltm_trial == 'attended_4' & ltm_image %notin% test1  ~ "unattended",
                                 ltm_trial == 'attended_5' & ltm_image %notin% test1  ~ "unattended"))

data_LTM_V3 <- data_LTM_V3 %>%
  group_by(participant)%>%
  mutate(testing = case_when(ltm_trial == 'attended_1' & ltm_image %in%  test1 ~ "tested",
                                 ltm_trial == 'attended_2' & ltm_image %in%  test1 ~ "tested",
                                 ltm_trial == 'attended_3' & ltm_image %in%  test1 ~ "tested",
                                 ltm_trial == 'attended_4' & ltm_image %in%  test1 ~ "tested",
                                 ltm_trial == 'attended_5' & ltm_image %in%  test1 ~ "tested",
                                 ltm_trial == 'unattended' & ltm_image %in%  test1 ~ "tested",
                                 ltm_trial == 'unattended' & ltm_image %notin% test1  ~ "not-tested",
                                 ltm_trial == 'attended_1' & ltm_image %notin% test1  ~ "not-tested",
                                 ltm_trial == 'attended_2' & ltm_image %notin% test1  ~ "not-tested",
                                 ltm_trial == 'attended_3' & ltm_image %notin% test1  ~ "not-tested",
                                 ltm_trial == 'attended_4' & ltm_image %notin% test1  ~ "not-tested",
                                 ltm_trial == 'attended_5' & ltm_image %notin% test1  ~ "not-tested"))

data_LTM_V3 <- data_LTM_V3 %>%
  group_by(participant)%>%
  mutate(image_effect = case_when(ltm_trial == 'attended_1' & ltm_image %in%  test1 & ltm_image %in%  image1 ~ "Image1-attended",
                                  ltm_trial == 'attended_2' & ltm_image %in%  test1 & ltm_image %in%  image1 ~ "Image1-attended",
                                  ltm_trial == 'attended_3' & ltm_image %in%  test1 & ltm_image %in%  image1 ~ "Image1-attended",
                                  ltm_trial == 'attended_1' & ltm_image %in%  test1 & ltm_image %in%  image2 ~ "Image2-attended",
                                  ltm_trial == 'attended_2' & ltm_image %in%  test1 & ltm_image %in%  image2 ~ "Image2-attended",
                                  ltm_trial == 'attended_3' & ltm_image %in%  test1 & ltm_image %in%  image2 ~ "Image2-attended",
                                  ltm_trial == 'attended_4' & ltm_image %in%  test1 & ltm_image %in%  image2 ~ "Image2-attended",
                                  ltm_trial == 'attended_5' & ltm_image %in%  test1 & ltm_image %in%  image2 ~ "Image2-attended",
                                  ltm_trial == 'attended_4' & ltm_image %in%  test1 & ltm_image %in%  image1 ~ "Image1-attended",
                                  ltm_trial == 'attended_5' & ltm_image %in%  test1 & ltm_image %in%  image1 ~ "Image1-attended",
                                  ltm_trial == 'unattended' & ltm_image %in%  test1 & ltm_image %in%  image1 ~ "Image1-unattended",
                                  ltm_trial == 'unattended' & ltm_image %in%  test1 & ltm_image %in%  image2 ~ "Image2-unattended",
                                  ltm_trial == 'unattended' & ltm_image %notin% test1 & ltm_image %in%  image2 ~ "Image2-attended-never tested",
                                  ltm_trial == 'unattended' & ltm_image %notin% test1 & ltm_image %in%  image1 ~ "Image1-attended-never tested",
                                  ltm_trial == 'attended_1' & ltm_image %notin% test1 & ltm_image %in%  image2 ~ "Image2-unattended-never tested",
                                  ltm_trial == 'attended_1' & ltm_image %notin% test1 & ltm_image %in%  image1 ~ "Image1-unattended-never tested",
                                  ltm_trial == 'attended_2' & ltm_image %notin% test1 & ltm_image %in%  image2 ~ "Image2-unattended-never tested",
                                  ltm_trial == 'attended_2' & ltm_image %notin% test1 & ltm_image %in%  image1 ~ "Image1-unattended-never tested",
                                  ltm_trial == 'attended_3' & ltm_image %notin% test1 & ltm_image %in%  image2 ~ "Image2-unattended-never tested",
                                  ltm_trial == 'attended_3' & ltm_image %notin% test1 & ltm_image %in%  image1 ~ "Image1-unattended-never tested",
                                  ltm_trial == 'attended_4' & ltm_image %notin% test1 & ltm_image %in%  image2 ~ "Image2-unattended-never tested",
                                  ltm_trial == 'attended_4' & ltm_image %notin% test1 & ltm_image %in%  image1 ~ "Image1-unattended-never tested",
                                  ltm_trial == 'attended_5' & ltm_image %notin% test1 & ltm_image %in%  image2 ~ "Image2-unattended-never tested",
                                  ltm_trial == 'attended_5' & ltm_image %notin% test1 & ltm_image %in%  image1 ~ "Image1-unattended-never tested"))

#remove extra WM rows again
data_LTM_V3 <- data_LTM_V3[rowSums(is.na(data_LTM_V3)) == 0|rowSums(is.na(data_LTM_V3)) == 1| rowSums(is.na(data_LTM_V3)) == 2|rowSums(is.na(data_LTM_V3)) == 3|rowSums(is.na(data_LTM_V3)) == 4,]

count_above_15 <- data_LTM_V3 %>%
  group_by(participant)%>%
  filter((timeout_ltm) == "1") %>%
  nrow()

count_above_15 <- data_LTM_V3 %>%
  filter(timeout_ltm == "1") %>%
  group_by(participant) %>%
  summarise(trials_count = n())

timeout_WM <- data_WM_V3 %>% filter(is.na(adjust_keys_t1.rt))
total_excluded_trials <- nrow(timeout_WM)

data_LTM_V3 <- data_LTM_V3[!(as.character(data_LTM_V3$timeout_ltm) == "1"), ]

```

 RIDER3 (manuscript RIDER2)

```{r RIDER3 pruning, echo=FALSE,include=FALSE}

data_WM_V3 <- data_WM_V3 %>% filter(!is.na(adjust_keys_t1.rt))

objects_time_out <- timeout_WM %>%
  group_by(participant,trial_type_new)%>%
  summarise(image1,image2)


objects_time_out<- objects_time_out %>% pivot_longer(cols=c('image1', 'image2'),names_to='Presentation',values_to='image1') 

# identification of ltm object pool that includes only pruned WM conditions (Test 1 and Test 2 is effected here)
data_LTM_V3 <- rbind.fill(data_LTM_V3,objects_time_out[c("participant", "image1")])

data_LTM_V3 <- data_LTM_V3 %>%
  group_by(participant)%>%
  mutate(matching = case_when(ltm_image %in% image1  ~ "Match",
                              ltm_image %notin%  image1  ~   "NO_Match"))


data_LTM_V3 <- data_LTM_V3[rowSums(is.na(data_LTM_V3)) == 1|rowSums(is.na(data_LTM_V3)) == 2|rowSums(is.na(data_LTM_V3)) == 3|rowSums(is.na(data_LTM_V3)) == 4,]

# delete all matching trials in ltm dataframe
data_LTM_V3<-data_LTM_V3[!(data_LTM_V3$matching=="Match"),]
removed_trials <-data.frame(matrix(ncol=22,nrow=0, dimnames=list(NULL, colnames(data_WM_V3))))

data_WM_after_pruning <- data_WM_V3

######current approach
for (i in data_WM_V3$participant){
  # select trials per participant
  attended_trials <- data_WM_V3[which(data_WM_V3$trial_type_new=='attended' & data_WM_V3$participant == i), ]
  unattended_trials <- data_WM_V3[which(data_WM_V3$trial_type_new=='unattended' & data_WM_V3$participant == i), ]
  # order mean values for each trial type to know what to prune
  vector <- c(mean(attended_trials$accuracy_t1,na.rm = TRUE),mean(unattended_trials$accuracy_t1,na.rm = TRUE))
  # find the reference for pruning (will be baseline for most participants)
  lowest <- mean(vector)+2
  # order the single values to prepare to remove them to equalize the means
  attended_trials <- attended_trials[order(attended_trials$accuracy_t1,decreasing = TRUE),]
  unattended_trials <- unattended_trials[order(unattended_trials$accuracy_t1,decreasing = TRUE),]
  while (mean(attended_trials$accuracy_t1,na.rm = TRUE) > lowest){
    removed <- attended_trials[1,]
    attended_trials <- attended_trials[-1,]
    removed_trials[nrow(removed_trials) + 1, ] <- removed
  }
  while (mean(unattended_trials$accuracy_t1,na.rm = TRUE) > lowest){
    removed <- unattended_trials[1,]
    unattended_trials <- unattended_trials[-1,]
    removed_trials[nrow(removed_trials) + 1, ] <- removed
  }
  print(i)
}

removed_trials <- removed_trials[!duplicated(removed_trials[,]),]

df_pruned <- data_WM_V3 %>%
  anti_join(removed_trials, by = c("participant" = "participant", "log_response_t1.rt" = "log_response_t1.rt",  "image_effect" = "image_effect"))

dataframe1 <- anti_join(data_WM_V3, removed_trials)

final_accuracy_summary <- dataframe1 %>%
  group_by(participant, trial_type_new) %>%
  summarize(mean_accuracy = mean(accuracy_t1, na.rm = TRUE))

objects <- removed_trials %>%
  group_by(participant,trial_type_new)%>%
  summarise(image1, image2)

objects<- objects %>% pivot_longer(cols=c('image1', 'image2'),names_to='Presentation',values_to='test1') 

# identification of ltm object pool that includes only pruned WM conditions (Test 1 and Test 2 is effected here)
data_LTM_V3 <- rbind.fill(data_LTM_V3,objects[c("participant", "test1")])

data_LTM_V3 <- data_LTM_V3 %>%
  group_by(participant)%>%
  mutate(matching = case_when(ltm_image %in% test1  ~ "Match",
                              ltm_image %notin%  test1  ~   "NO_Match"))


data_LTM_V3 <- data_LTM_V3[rowSums(is.na(data_LTM_V3)) == 1|rowSums(is.na(data_LTM_V3)) == 2|rowSums(is.na(data_LTM_V3)) == 3|rowSums(is.na(data_LTM_V3)) == 4,]

# delete all matching trials in ltm dataframe
data_LTM_pruned_V3<-data_LTM_V3[!(data_LTM_V3$matching=="Match"),]

```

RIDER3 summary dataframes for plotting (note in manuscript this would be experiment 2)
 1) Participant means (here not printed)
 2) Sample means per condition (printed for an overview)
 
```{r RIDER3 summary, echo=FALSE}

##WM 
# WM Sample presentation plot preparation

summary_stats_participant_image_pres <- summarySE(data_WM_V3, measurevar = "accuracy_t1", groupvars = c("image_effect","participant"),na.rm = T)
summary_study_level_image_pres <- summarySE(summary_stats_participant_image_pres, measurevar = "accuracy_t1", groupvars = c("image_effect"),na.rm = T)
summary_study_level_image_pres$participant <- 1
# Convert 'participant' to a factor explicitly
summary_stats_participant_image_pres$participant <- factor(summary_stats_participant_image_pres$participant)
summary_study_level_image_pres$participant <- factor(summary_study_level_image_pres$participant)
level_order9 <- c('Image1-attended', 'Image2-attended','Image1-unattended','Image2-unattended') 


print("Sample means Working Memory")
summary_study_level_image_pres

## LTM
summary_stats_participant_LTM_p_V3 <- summarySE(data_LTM_pruned_V3, measurevar = "accuracy_ltm", groupvars = c("image_effect","participant"),na.rm = T)

summary_study_level_LTM_p_V3 <- summarySE(summary_stats_participant_LTM_p_V3, measurevar = "accuracy_ltm", groupvars = c("image_effect"),na.rm = T)


summary_study_level_LTM_p_V3$participant <- 1
summary_stats_participant_LTM_p_V3$participant <- factor(summary_stats_participant_LTM_p_V3$participant)
summary_study_level_LTM_p_V3$participant <- factor(summary_study_level_LTM_p_V3$participant)

print("Pruned sample means Long-term Memory")
summary_study_level_LTM_p_V3

```



