---
title: "RIDER Experiment 2"
output:
  html_document:
    theme: sandstone
    toc: yes
    toc_depth: '1'
    df_print: paged

date: "2024-07-15"
author: Frieda Born
e-mail: born@mpib-berlin.mpg.de
---

This document provides an the statistical tests provided in the paper ordered along the sub sections of our publication. We investigate how testing and (de)prioritization during **Working** **Memory** influences how well something sticks to **Long-term** **Memory**. In the following you find the results for *RIDER2*, which constitutes the results of a classical **retro-cue** **paradigm**, which we tested as an alternative priority manipulation. 
There are separate documents proving the statistical tests for Exp. 1 & Exp. 3 (see RIDER1_stats.Rmd & RIDER3_stats.Rmd).
<br>
<br>
<br>

```{r setup environment, include=FALSE,fig.dim = c(4, 2)}
knitr::opts_chunk$set(echo = TRUE)
# surpress warnings
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
#clean environment
rm(list = ls()) 

#Libraries
library(plyr) #Ssplitting, applying and combining Data
library(dplyr) # for general data manipulation
library(ggplot2) # for visualizations
library(purrr)#working with functions and vectors
library(stringr)#working with strings
library(purrr)# for plotting
library(tidyverse)#different aspects of data processing
library(reshape)# for general data manipulation
library(scico)#colour palettes fpr plotting
library("readxl")
library(circular)
library(Rmisc)
library(ggpubr)# for plotting
library(rstatix)#for stats
library(viridis)# for nice plotting colors
library(data.table)
library(BayesFactor)#for performing a Bayesian t-test
library(cowplot)#for plotting
library(ggstatsplot)
library(formatR)
library(PupillometryR)
library(sm)
library(hrbrthemes)#nice plotting
library(viridis)#nice plotting
library(gridExtra)
library(plotly)# intersczive plotting
 library(ggpubr)
`%notin%` <- Negate(`%in%`)
```

```{r loading data, include=FALSE}
# RIDER2 data
data_WM_V3 <- read.csv("path/to/data/location/data/WM_data_RIDER_2.csv",na.strings=c("","NA"))
data_LTM_V3 <- read.csv("path/to/data/location/data/LTM_data_RIDER_2.csv",na.strings=c("","NA"))
```


```{r identifying missed trials and removing them, include=FALSE}
### Processing of WM data (exp. trial selection, exp. condition identification, accuracy calculation)
data_WM_V3<-data_WM_V3[!(data_WM_V3$participant==63),]
data_LTM_V3<-data_LTM_V3[!(data_LTM_V3$participant==63),]
# For methods part here we calculate the percentage of responses that were given outside the predefined time window of 15s
count_above_15 <- data_LTM_V3 %>%
  filter(timeout_ltm == "1") %>%
  group_by(participant) %>%
  summarise(trials_count = n())

total_participants <- 89
trials_per_participant <- 112
# 
# # Calculate the average number of trials per participant
average_trials_per_participant <- sum(count_above_15$trials_count) / total_participants

# # Calculate the minimum and maximum percentages
min_percentage <- (0 / trials_per_participant) * 100
max_percentage <- (max(count_above_15$trials_count) / trials_per_participant) * 100
# 
# # Format the result
print("on average participants missed 0.472 % of the trials in LTM, min. 0% and max 14.29%")

# Calculate the same for WM task
# Group the data by participant and remove the first 6 trials for each participant
data_WM_V3 <- data_WM_V3 %>%
  group_by(participant) %>%
  slice(7:n()) %>%
  ungroup()

# Identify the row indices that have been deleted
practice_trials <- data_WM_V3 %>%
  group_by(participant) %>%
  slice(1:6)

timeout_WM <- data_WM_V3 %>% filter(is.na(adjust_keys_t1.rt))


total_excluded_trials <- nrow(timeout_WM)

# Calculate the average number of trials per participant
average_trials_per_participant_WM <- total_excluded_trials / total_participants

trials_per_participant <- 56

# # Calculate the minimum and maximum percentages
min_percentage <- (0 / trials_per_participant) * 100
count_levels <- timeout_WM %>%
  count(participant)
max_percentage <- (max(count_levels$n) / trials_per_participant) * 100
# 
# Format the result
print("For WM we have the following stats of missed reponses. Average:")
average_trials_per_participant_WM
print("Min = 0 % and max:")
max_percentage 

# removing timeout trials from LTM to continiue with stats analysis
data_LTM_V3 <- data_LTM_V3[!(as.character(data_LTM_V3$timeout_ltm) == "1"), ]

```


```{r calculating accurcy RIDER2 WM and LTM , include=FALSE}


#calculating the correct fixed orientations for the 2-item trials:
#depending on whether the stimulus was presented in image 1 or image 2
data_WM_V3$startOri1 <- as.character(data_WM_V3$startOri1)

# here I determine the orientation the test image was presented in and give it the name fixedOri_t1
data_WM_V3 <- data_WM_V3 %>%
  rowwise() %>%
  mutate(
    fixedOri_t1 = case_when(
      test1 == image1 ~ as.numeric(startOri1),
      test1 == image2 ~ as.numeric(startOri2),
      TRUE ~ NA_real_
    )
  )
# calculate remainder of this_ori variable to adjust for cases that are beyond 360 degrees
data_WM_V3 <- data_WM_V3 %>% mutate(ori_t1_corrected = this_ori_t1 %% 360)#Modulus (Remainder from division)

# converting to numerical 
data_WM_V3$fixedOri_t1 <- as.numeric(data_WM_V3$fixedOri_t1)

# calculating accuracy
# function
angdiff <- function(alpha_deg, beta_deg) {
  #The function assumes that the input angles alpha and beta are in radians.So, you will have to convert them to radians first:
  alpha_rad <- alpha_deg * pi / 180
  beta_rad <- beta_deg * pi / 180
  # Then, you calculate the difference in angles
  delta_rad <- alpha_rad - beta_rad
  # If your input angles alpha and beta are larger than 360°, the mod() function will correctly wrap them to the range of [-180,180] degrees interval.
  delta_rad <- (delta_rad + pi) %% (2*pi) - pi
  delta_deg <- delta_rad * 180 / pi
  #the function outputs both the angular difference in degrees and in radians
  return(list(delta_rad = delta_rad, delta_deg = delta_deg))
}

# accuracy in radians for WM
data_WM_V3$accuracy_t1_rad <- apply(data_WM_V3[,c("this_ori_t1", "fixedOri_t1")], 1, function(x) angdiff(x[1], x[2])$delta_rad)

# accuracy in degrees
data_WM_V3$accuracy_t1 <- abs(apply(data_WM_V3[,c("this_ori_t1", "fixedOri_t1")], 1, function(x) angdiff(x[1], x[2])$delta_deg))


# calculate ltm accuracy for WM
data_LTM_V3 <- data_LTM_V3 %>% mutate(ori_ltm = this_ori_ltm %% 360)#Modulus (Remainder from division)

# calculating accuracy for LTM test
data_LTM_V3 <- data_LTM_V3 %>% 
  rowwise() %>%
  mutate(min_angle_ltm = abs(ori_ltm -fixedOri_ltm))%>%
  mutate(max_angle_ltm = 360-abs(ori_ltm -fixedOri_ltm))

data_LTM_V3 <- transform(data_LTM_V3, accuracy_ltm = pmin(min_angle_ltm, max_angle_ltm))#angular difference
#radians
data_LTM_V3$accuracy_ltm_rad <- (apply(data_LTM_V3[,c("this_ori_ltm", "fixedOri_ltm")], 1, function(x) angdiff(x[1], x[2])$delta_rad))

```

```{r renaming trial types RIDER3 for WM and LTM, echo=FALSE}
data_WM_V3 <- data_WM_V3  %>% 
  mutate(trial_type_new = case_when(
    trial_type == "attended_1" ~ "attended",
    trial_type == "attended_2" ~ "attended",
    trial_type == "attended_3" ~ "attended",
    trial_type == "attended_4" ~ "attended",
    trial_type == "attended_5" ~ "attended",
    trial_type == "unattended" ~ "unattended"))


data_WM_V3 <- data_WM_V3  %>% 
  mutate(image_effect = case_when(
    trial_type == "attended_1" & image1 %in%  test1 ~ "Image1-attended",
    trial_type == "attended_1" & image2 %in%  test1 ~ "Image2-attended",
    trial_type == "attended_2" & image1 %in%  test1 ~ "Image1-attended",
    trial_type == "attended_2" & image2 %in%  test1 ~ "Image2-attended",
    trial_type == "attended_3" & image1 %in%  test1 ~ "Image1-attended",
    trial_type == "attended_3" & image2 %in%  test1 ~ "Image2-attended",
    trial_type == "attended_4" & image1 %in%  test1 ~ "Image1-attended",
    trial_type == "attended_4" & image2 %in%  test1 ~ "Image2-attended",
    trial_type == "attended_5" & image1 %in%  test1 ~ "Image1-attended",
    trial_type == "attended_5" & image2 %in%  test1 ~ "Image2-attended",
    trial_type == "unattended" & image1 %in%  test1 ~ "Image1-unattended",
    trial_type == "unattended" & image2 %in%  test1 ~ "Image2-unattended",))

# we need the WM information to determine the trial types in LTM, so we are doing this here
data_LTM_V3 <- rbind.fill(data_LTM_V3,data_WM_V3[c("test1","participant","image1","image2")])

# simple trial types NP, tested, attended, unattended
data_LTM_V3 <- data_LTM_V3 %>%
  group_by(participant)%>%
  mutate(trial_type = case_when(ltm_trial == 'attended_1' & ltm_image %in%  test1 ~ "attended",
                                 ltm_trial == 'attended_2' & ltm_image %in%  test1 ~ "attended",
                                 ltm_trial == 'attended_3' & ltm_image %in%  test1 ~ "attended",
                                 ltm_trial == 'attended_4' & ltm_image %in%  test1 ~ "attended",
                                 ltm_trial == 'attended_5' & ltm_image %in%  test1 ~ "attended",
                                 ltm_trial == 'unattended' & ltm_image %in%  test1 ~ "unattended",
                                 ltm_trial == 'unattended' & ltm_image %notin% test1  ~ "attended-never tested",
                                 ltm_trial == 'attended_1' & ltm_image %notin% test1  ~ "unattended-never tested",
                                 ltm_trial == 'attended_2' & ltm_image %notin% test1  ~ "unattended-never tested",
                                 ltm_trial == 'attended_3' & ltm_image %notin% test1  ~ "unattended-never tested",
                                 ltm_trial == 'attended_4' & ltm_image %notin% test1  ~ "unattended-never tested",
                                 ltm_trial == 'attended_5' & ltm_image %notin% test1  ~ "unattended-never tested"))

# for later stats create column that shows if items were prioritized (attended) in WM
data_LTM_V3 <- data_LTM_V3 %>%
  group_by(participant)%>%
  mutate(attention = case_when(ltm_trial == 'attended_1' & ltm_image %in%  test1 ~ "attended",
                                 ltm_trial == 'attended_2' & ltm_image %in%  test1 ~ "attended",
                                 ltm_trial == 'attended_3' & ltm_image %in%  test1 ~ "attended",
                                 ltm_trial == 'attended_4' & ltm_image %in%  test1 ~ "attended",
                                 ltm_trial == 'attended_5' & ltm_image %in%  test1 ~ "attended",
                                 ltm_trial == 'unattended' & ltm_image %in%  test1 ~ "unattended",
                                 ltm_trial == 'unattended' & ltm_image %notin% test1  ~ "attended",
                                 ltm_trial == 'attended_1' & ltm_image %notin% test1  ~ "unattended",
                                 ltm_trial == 'attended_2' & ltm_image %notin% test1  ~ "unattended",
                                 ltm_trial == 'attended_3' & ltm_image %notin% test1  ~ "unattended",
                                 ltm_trial == 'attended_4' & ltm_image %notin% test1  ~ "unattended",
                                 ltm_trial == 'attended_5' & ltm_image %notin% test1  ~ "unattended"))

# for later stats create column that shows if items were tested in WM or not
data_LTM_V3 <- data_LTM_V3 %>%
  group_by(participant)%>%
  mutate(testing = case_when(ltm_trial == 'attended_1' & ltm_image %in%  test1 ~ "tested",
                                 ltm_trial == 'attended_2' & ltm_image %in%  test1 ~ "tested",
                                 ltm_trial == 'attended_3' & ltm_image %in%  test1 ~ "tested",
                                 ltm_trial == 'attended_4' & ltm_image %in%  test1 ~ "tested",
                                 ltm_trial == 'attended_5' & ltm_image %in%  test1 ~ "tested",
                                 ltm_trial == 'unattended' & ltm_image %in%  test1 ~ "tested",
                                 ltm_trial == 'unattended' & ltm_image %notin% test1  ~ "not-tested",
                                 ltm_trial == 'attended_1' & ltm_image %notin% test1  ~ "not-tested",
                                 ltm_trial == 'attended_2' & ltm_image %notin% test1  ~ "not-tested",
                                 ltm_trial == 'attended_3' & ltm_image %notin% test1  ~ "not-tested",
                                 ltm_trial == 'attended_4' & ltm_image %notin% test1  ~ "not-tested",
                                 ltm_trial == 'attended_5' & ltm_image %notin% test1  ~ "not-tested"))


data_LTM_V3 <- data_LTM_V3 %>%
  group_by(participant)%>%
  mutate(image_effect = case_when(ltm_trial == 'attended_1' & ltm_image %in%  test1 & ltm_image %in%  image1 ~ "Image1-attended",
                                  ltm_trial == 'attended_2' & ltm_image %in%  test1 & ltm_image %in%  image1 ~ "Image1-attended",
                                  ltm_trial == 'attended_3' & ltm_image %in%  test1 & ltm_image %in%  image1 ~ "Image1-attended",
                                  ltm_trial == 'attended_1' & ltm_image %in%  test1 & ltm_image %in%  image2 ~ "Image2-attended",
                                  ltm_trial == 'attended_2' & ltm_image %in%  test1 & ltm_image %in%  image2 ~ "Image2-attended",
                                  ltm_trial == 'attended_3' & ltm_image %in%  test1 & ltm_image %in%  image2 ~ "Image2-attended",
                                  ltm_trial == 'attended_4' & ltm_image %in%  test1 & ltm_image %in%  image2 ~ "Image2-attended",
                                  ltm_trial == 'attended_5' & ltm_image %in%  test1 & ltm_image %in%  image2 ~ "Image2-attended",
                                  ltm_trial == 'attended_4' & ltm_image %in%  test1 & ltm_image %in%  image1 ~ "Image1-attended",
                                  ltm_trial == 'attended_5' & ltm_image %in%  test1 & ltm_image %in%  image1 ~ "Image1-attended",
                                  ltm_trial == 'unattended' & ltm_image %in%  test1 & ltm_image %in%  image1 ~ "Image1-unattended",
                                  ltm_trial == 'unattended' & ltm_image %in%  test1 & ltm_image %in%  image2 ~ "Image2-unattended",
                                  ltm_trial == 'unattended' & ltm_image %notin% test1 & ltm_image %in%  image2 ~ "Image2-attended-never tested",
                                  ltm_trial == 'unattended' & ltm_image %notin% test1 & ltm_image %in%  image1 ~ "Image1-attended-never tested",
                                  ltm_trial == 'attended_1' & ltm_image %notin% test1 & ltm_image %in%  image2 ~ "Image2-unattended-never tested",
                                  ltm_trial == 'attended_1' & ltm_image %notin% test1 & ltm_image %in%  image1 ~ "Image1-unattended-never tested",
                                  ltm_trial == 'attended_2' & ltm_image %notin% test1 & ltm_image %in%  image2 ~ "Image2-unattended-never tested",
                                  ltm_trial == 'attended_2' & ltm_image %notin% test1 & ltm_image %in%  image1 ~ "Image1-unattended-never tested",
                                  ltm_trial == 'attended_3' & ltm_image %notin% test1 & ltm_image %in%  image2 ~ "Image2-unattended-never tested",
                                  ltm_trial == 'attended_3' & ltm_image %notin% test1 & ltm_image %in%  image1 ~ "Image1-unattended-never tested",
                                  ltm_trial == 'attended_4' & ltm_image %notin% test1 & ltm_image %in%  image2 ~ "Image2-unattended-never tested",
                                  ltm_trial == 'attended_4' & ltm_image %notin% test1 & ltm_image %in%  image1 ~ "Image1-unattended-never tested",
                                  ltm_trial == 'attended_5' & ltm_image %notin% test1 & ltm_image %in%  image2 ~ "Image2-unattended-never tested",
                                  ltm_trial == 'attended_5' & ltm_image %notin% test1 & ltm_image %in%  image1 ~ "Image1-unattended-never tested"))



#remove extra WM rows again
data_LTM_V3 <- data_LTM_V3[rowSums(is.na(data_LTM_V3)) == 0|rowSums(is.na(data_LTM_V3)) == 1| rowSums(is.na(data_LTM_V3)) == 2|rowSums(is.na(data_LTM_V3)) == 3|rowSums(is.na(data_LTM_V3)) == 4,]

```

# Statistics

<h3 style="text-align: center; color: orange;">**WM Performance**</h3>
#### Pairwise comparisons and average accuracy across conditions
```{r pairwise t-test WM RIDER2, echo=FALSE}
print("The following pairwise t-test show the difference between attended and unattended storage in WM")

full_data_summary <-data_WM_V3 %>%
  group_by(trial_type_new, participant) %>%
  get_summary_stats(accuracy_t1, type = "mean_sd")

# Set the order of levels in the exp_condition factor
full_data_summary$trial_type_new <- factor(full_data_summary$trial_type_new, levels = c("unattended", "attended"))

summary_stats_participant_trial_type_V3 <- summarySE(data_WM_V3, measurevar = "accuracy_t1", groupvars = c("trial_type_new","participant"),na.rm = T)
summary_study_level_trial_type_V3 <- summarySE(summary_stats_participant_trial_type_V3, measurevar = "accuracy_t1", groupvars = c("trial_type_new"),na.rm = T)

full_data_summary %>%
  pairwise_t_test(
    mean ~ trial_type_new, paired = TRUE,
    p.adjust.method = "holm")
```


### ANOVA Results WM 
#### (2 x 2 ANOVA Cueing (cued/uncued) and Sample Position (1/2)
```{r 2x2 ANOVA cueing - sample position WM, echo=FALSE}
print("WM: This 2x2 ANOVA checks for effects of the factors Cueing (cued/uncued) and Sample Position (1/2)")

data_WM_V3$test <-"WM"

data_subset_WM <- data_WM_V3%>%
  select(accuracy_t1, trial_type_new,image_effect,participant,test)

data_subset_WM <- data_subset_WM %>%
  filter(image_effect %in% c("Image1-attended", "Image1-unattended", "Image2-attended", "Image2-unattended"))

# Step 2: Further filter rows based on exp_condition and task
data_subset_WM <- data_subset_WM %>%
  filter(trial_type_new %in% c("attended", "unattended"))

# Step 3: Rename variable levels
data_subset_WM <- data_subset_WM %>%
  mutate(image_effect = sub("-attended$", "", image_effect),
         image_effect = sub("-unattended$", "", image_effect))

summary_image_pres <-data_subset_WM %>%
  group_by(trial_type_new, participant,image_effect) %>%
  get_summary_stats(accuracy_t1, type = "mean_sd")

summary_image_pres$trial_type_new <- factor(summary_image_pres$trial_type_new)
summary_image_pres$image_effect <- factor(summary_image_pres$image_effect)

res.aov_image_presWM <- anova_test(data = summary_image_pres, dv = mean, wid = participant, within = c(image_effect,trial_type_new))

get_anova_table(res.aov_image_presWM)


```
<h3 style="text-align: center; color: blue;">**LTM Performance**</h3>

#### Mean performances across conditions
```{r LTM mean performances, echo=FALSE}
print("Mean performance across experiment conditions")
summary_stats_participant_LTM_V3 <- summarySE(data_LTM_V3, measurevar = "accuracy_ltm", groupvars = c("trial_type","participant"),na.rm = T)
summary_study_level_LTM_V3 <- summarySE(summary_stats_participant_LTM_V3, measurevar = "accuracy_ltm", groupvars = c("trial_type"),na.rm = T)
summary_study_level_LTM_V3

# perform t test to compare LTM performance in Exp. 1 and 2 - > this will be commented out here because this script only deals with anaylsis of Exp. 2 data
# Separate the data into two vectors
# summary_stats_participant_LTM2 <- summarySE(summary_stats_participant_LTM, measurevar = "accuracy_ltm", groupvars = c("participant"),na.rm = T)
# summary_stats_participant_LTM_V32 <- summarySE(summary_stats_participant_LTM_V3, measurevar = "accuracy_ltm", groupvars = c("participant"),na.rm = T)
# 
# accuracy_exp1 <- summary_stats_participant_LTM2 %>% pull(accuracy_ltm)
# accuracy_exp2 <- summary_stats_participant_LTM_V32 %>% pull(accuracy_ltm)
# 
# # Perform paired t-test
# t_test_result <- t.test(accuracy_exp1, accuracy_exp2, paired = FALSE)
# 
# # Print the result
# print(t_test_result)


print("General mean performance of LTM performance in Exp. 2")
mean(summary_study_level_LTM_V3$accuracy_ltm)

print("T-test result for difference between probed and unprobed information")

data_LTM_V3 <- data_LTM_V3 %>%
  mutate(
    probed = case_when(
      trial_type %in% c("attended", "unattended") ~ "probed",
      trial_type %in% c("attended-never tested", "unattended-never tested") ~ "NP",
      TRUE ~ as.character(trial_type)
    )
  )

summary_probing <- summarySE(
  data_LTM_V3,
  measurevar = "accuracy_ltm",
  groupvars = c("probed","participant"),
  na.rm = TRUE
)

# Separate the data into two vectors
accuracy_ltm_yes <- summary_probing %>% filter(probed == "probed") %>% pull(accuracy_ltm)
accuracy_ltm_no <- summary_probing %>% filter(probed == "NP") %>% pull(accuracy_ltm)

# Perform paired t-test
t_test_result <- t.test(accuracy_ltm_yes, accuracy_ltm_no, paired = TRUE)

# Print the result
print(t_test_result)

```
#### Pairwise comparisons for Cueing and Testing conditions

```{r LTM Performance - > pairwise comparisons, echo=FALSE}
print("The pairwise comparisons show sig. better performance in probed vs. unprobed information")
full_data_summary_ltm_V3 <-data_LTM_V3 %>%
  group_by(trial_type, participant) %>%
  get_summary_stats(accuracy_ltm, type = "mean_sd")


full_data_summary_ltm_V3 %>%
  pairwise_t_test(
    mean ~ trial_type, paired = TRUE,
    p.adjust.method = "holm")


```
<br>
<br>
<br>
### ANOVA Results LTM (unpruned)
Turning to the LTM consequences of WM cueing, we first inspected the full data (i.e., without pruning) irrespective of the differences in WM performance between cued and uncued samples.
#### (2 x 2 ANOVA WM Testing (tested vs. NP) and Cueing (cued/uncued) 

```{r 2 x2 ANOVA unpruned, echo=FALSE}

print("2x2 ANOVA for factors of probing and cueing")

two_x_two_LTM <-data_LTM_V3 %>%
  group_by(attention, testing, participant) %>%
  get_summary_stats(accuracy_ltm, type = "mean_sd")


# Calculate participant means
two_x_two_LTM <- data_LTM_V3 %>%
  group_by(attention, testing, participant) %>%
  summarise(participant_mean = mean(accuracy_ltm)) %>%
  ungroup()

# Calculate overall mean
overall_mean <- two_x_two_LTM %>%
  group_by(attention, testing) %>%
  summarise(overall_mean = mean(participant_mean))

res.aov <- anova_test(data = two_x_two_LTM, dv = participant_mean, wid = participant, within = c(attention, testing))

get_anova_table(res.aov)

```

```{r pruning and WM bias RIDER3, include=FALSE}
timeout_WM <- data_WM_V3 %>% filter(is.na(adjust_keys_t1.rt))

data_WM_V3 <- data_WM_V3 %>% filter(!is.na(adjust_keys_t1.rt))

objects_time_out <- timeout_WM %>%
  group_by(participant,trial_type_new)%>%
  summarise(image1,image2)

# I am removing the trials from the LTM data were WM trials timed out
objects_time_out<- objects_time_out %>% pivot_longer(cols=c('image1', 'image2'),names_to='Presentation',values_to='image1') 

# identification of ltm object pool that includes only pruned WM conditions (Test 1 and Test 2 is effected here)
data_LTM_V3 <- rbind.fill(data_LTM_V3,objects_time_out[c("participant", "image1")])

data_LTM_V3 <- data_LTM_V3 %>%
  group_by(participant)%>%
  mutate(matching = case_when(ltm_image %in% image1  ~ "Match",
                              ltm_image %notin%  image1  ~   "NO_Match"))


data_LTM_V3 <- data_LTM_V3[rowSums(is.na(data_LTM_V3)) == 1|rowSums(is.na(data_LTM_V3)) == 2|rowSums(is.na(data_LTM_V3)) == 3|rowSums(is.na(data_LTM_V3)) == 4,]

# delete all matching trials in ltm dataframe
data_LTM_V3<-data_LTM_V3[!(data_LTM_V3$matching=="Match"),]


## I am pruning the data
removed_trials <-data.frame(matrix(ncol=23,nrow=0, dimnames=list(NULL, colnames(data_WM_V3))))

data_WM_after_pruning <- data_WM_V3
######current approach
for (i in data_WM_V3$participant){
  # select trials per participant
  attended_trials <- data_WM_V3[which(data_WM_V3$trial_type_new=='attended' & data_WM_V3$participant == i), ]
  unattended_trials <- data_WM_V3[which(data_WM_V3$trial_type_new=='unattended' & data_WM_V3$participant == i), ]
  # order mean values for each trial type to know what to prune
  vector <- c(mean(attended_trials$accuracy_t1,na.rm = TRUE),mean(unattended_trials$accuracy_t1,na.rm = TRUE))
  # find the reference for pruning (will be baseline for most participants)
  lowest <- mean(vector)+2
  # order the single values to prepare to remove them to equalize the means
  attended_trials <- attended_trials[order(attended_trials$accuracy_t1,decreasing = TRUE),]
  unattended_trials <- unattended_trials[order(unattended_trials$accuracy_t1,decreasing = TRUE),]
  while (mean(attended_trials$accuracy_t1,na.rm = TRUE) > lowest){
    removed <- attended_trials[1,]
    attended_trials <- attended_trials[-1,]
    removed_trials[nrow(removed_trials) + 1, ] <- removed
  }
  while (mean(unattended_trials$accuracy_t1,na.rm = TRUE) > lowest){
    removed <- unattended_trials[1,]
    unattended_trials <- unattended_trials[-1,]
    removed_trials[nrow(removed_trials) + 1, ] <- removed
  }
  print(i)
}

removed_trials <- removed_trials[!duplicated(removed_trials[,]),]


df_pruned <- data_WM_V3 %>%
  anti_join(removed_trials, by = c("participant" = "participant", "log_response_t1.rt" = "log_response_t1.rt",  "image_effect" = "image_effect"))

dataframe1 <- anti_join(data_WM_V3, removed_trials)

final_accuracy_summary <- dataframe1 %>%
  group_by(participant, trial_type_new) %>%
  summarize(mean_accuracy = mean(accuracy_t1, na.rm = TRUE))

objects <- removed_trials %>%
  group_by(participant,trial_type_new)%>%
  summarise(image1, image2)

objects<- objects %>% pivot_longer(cols=c('image1', 'image2'),names_to='Presentation',values_to='test1') 

# identification of ltm object pool that includes only pruned WM conditions (Test 1 and Test 2 is effected here)

data_LTM_V3 <- rbind.fill(data_LTM_V3,objects[c("participant", "test1")])

data_LTM_V3 <- data_LTM_V3 %>%
  group_by(participant)%>%
  mutate(matching = case_when(ltm_image %in% test1  ~ "Match",
                              ltm_image %notin%  test1  ~   "NO_Match"))


data_LTM_V3 <- data_LTM_V3[rowSums(is.na(data_LTM_V3)) == 1|rowSums(is.na(data_LTM_V3)) == 2|rowSums(is.na(data_LTM_V3)) == 3|rowSums(is.na(data_LTM_V3)) == 4,]

# delete all matching trials in ltm dataframe
data_LTM_pruned_V3<-data_LTM_V3[!(data_LTM_V3$matching=="Match"),]

```

<br>
<br>
<br>
<h3 style="text-align: center; color: lightblue;">**Pruned LTM performance**</h3>

First, let's have a look at the mean Error across conditions after pruning:
<br>
<br>
<br>
```{r accuracy LTM trial type PRUNED RIDER3, echo=FALSE,out.width="130%"}

summary_stats_participant_LTM_p_V3 <- summarySE(data_LTM_pruned_V3, measurevar = "accuracy_ltm", groupvars = c("trial_type","participant"),na.rm = T)

summary_study_level_LTM_p_V3 <- summarySE(summary_stats_participant_LTM_p_V3, measurevar = "accuracy_ltm", groupvars = c("trial_type"),na.rm = T)
summary_study_level_LTM_p_V3
```

#### Pairwise comparisons after pruning:
First, for the experiment conditions resulting from testing and cueing.
Second, WM sample position effect that indicate that we also find a primacy effect for (most) LTM exp. conditions in Exp. 2.

```{r pairwise t-test LTM pruned, echo=FALSE}
print("The following pairwise t-test tests the difference between attended, unattended and attended/unattended never tested storage in pruned LTM data")

full_data_summary_ltm_p_V3 <-data_LTM_pruned_V3 %>%
  group_by(trial_type, participant) %>%
  get_summary_stats(accuracy_ltm, type = "mean_sd")

full_data_summary_ltm_p_V3 <-data_LTM_pruned_V3 %>%
  group_by(trial_type, participant,image_effect) %>%
  get_summary_stats(accuracy_ltm, type = "mean_sd")


full_data_summary_ltm_p_V3 %>%
  pairwise_t_test(
    mean ~ trial_type, paired = TRUE,
    p.adjust.method = "holm")

full_data_summary_ltm_p_V3 %>%
  group_by(trial_type)%>%
  pairwise_t_test(
    mean ~ image_effect, paired = TRUE,
    p.adjust.method = "holm")

```


### ANOVA Results LTM (pruned)
#### (2 x 2 ANOVA WM Testing (tested vs. NP) and Cueing (cued/uncued) 
We repeated the analysis after pruning the data (see Exp.1 and Methods) to warrant equivalent WM performance for cued and uncued samples.
<br>
<br>
The 2x2 Design of Cueing x Testing allows us to examine slopes between untested **attended** and untested **un**attended.
After pruning, the LTM results showed a significant interaction of WM Testing and Cueing.
<br>
<br>
<br>
```{r ANOVA2 (pruned),echo=FALSE}

data_LTM_pruned_V3 <- data_LTM_pruned_V3  %>% 
   mutate(attention = case_when(
     trial_type == "attended" ~ "attended",
     trial_type == "unattended" ~ "unattended",
     trial_type == "unattended-never tested" ~ "unattended",
     trial_type == "attended-never tested" ~ "attended"))
 
data_LTM_pruned_V3 <- data_LTM_pruned_V3  %>% 
   mutate(testing = case_when(
     trial_type == "unattended-never tested" ~ "no",
     trial_type == "attended-never tested" ~ "no",
     trial_type == "attended" ~ "yes",
     trial_type == "unattended" ~ "yes"))


## next I want to look at a 2x2 ANOVA  in regard to the slope of the testing benefit in attention vs. unattention trials

# Calculate participant means
participant_means <- data_LTM_pruned_V3 %>%
  group_by(attention, testing, participant) %>%
  summarise(participant_mean = mean(accuracy_ltm)) %>%
  ungroup()

# Calculate overall mean
overall_mean <- participant_means %>%
  group_by(attention, testing) %>%
  summarise(overall_mean = mean(participant_mean))


res.aov <- anova_test(data = participant_means, dv = participant_mean, wid = participant, within = c(attention, testing))

get_anova_table(res.aov)


print("Here just the mean values over the ANOVA conditions")
overall_mean
```
### (2 x 2 x 2 ANOVA (WM Sample Position x Testing x Cueing) (again, in pruned data)
<br>
<br>
<br>

Further inspection of the LTM results with a 2 x 2 x 2 ANOVA (Sample Position x Testing x Cueing), showed a significant main effect of Sample Position indicating a primacy effect on LTM recall  (see also Exp. 1), but no additional new interactions.
```{r ANOVA including Sample position Effekts,echo=FALSE}

 
print("Repeated anaylsis in 2x2x2 design")

# I prepare the image_effect column for the anova
data_LTM_pruned_V3$image_effect <- sub("-.*", "", data_LTM_pruned_V3$image_effect)

participant_means_extended <- data_LTM_pruned_V3 %>%
  group_by(attention, testing, participant,image_effect) %>%
  summarise(participant_mean = mean(accuracy_ltm)) %>%
  ungroup()

# Calculate overall mean
overall_mean_extended  <- participant_means %>%
  group_by(attention, testing) %>%
  summarise(overall_mean = mean(participant_mean))


res.aov <- anova_test(data = participant_means_extended, dv = participant_mean, wid = participant, within = c(attention, testing,image_effect))

get_anova_table(res.aov)
```


```{r Additional analysis code,echo=FALSE}

##### The following code is not relevant for the stats reported in the papa, but allows for additional overview, which is why I am inclduing it here, commented out

# data_LTM_pruned_V3$task <- "LTM"
# data_WM_V3$task <-"WM"
# df_pruned$task <- "WM"
# 
# # creating the full_data df with the pruned WM data
# 
# data_subset <- data_LTM_pruned_V3 %>%
#   select(accuracy_ltm, trial_type,participant,task)
# 
# data_subset_WM <- df_pruned%>%
#   select(accuracy_t1, trial_type_new,participant,task)
# 
# data_subset_new <- data_LTM_pruned_V3 %>%
#   select(accuracy_ltm, trial_type,image_effect,participant,task)
# 
# data_subset_WM_new <- df_pruned%>%
#   select(accuracy_t1, trial_type_new,image_effect,participant,task)
# 
# colnames(data_subset)[1] = "accuracy_t1"
# colnames(data_subset)[2] = "exp_condition"
# colnames(data_subset_new)[2] = "exp_condition"
# colnames(data_subset_new)[1] = "accuracy_t1"
# colnames(data_subset_WM)[2] = "exp_condition"
# colnames(data_subset_WM_new)[2] = "exp_condition"
# 
# colnames(data_subset_new)[1] = "accuracy_t1"
# colnames(data_subset_new)[3] = "stimulus_effect"
# colnames(data_subset_WM_new)[3] = "stimulus_effect"
# 
# full_data <- rbind(data_subset_WM, data_subset)
# 
# full_data_new <- rbind(data_subset_WM_new, data_subset_new)
# 
# full_data<-full_data[!(full_data$exp_condition=="unattended-never tested"),]
# full_data<-full_data[!(full_data$exp_condition=="attended-never tested"),]
# 
# full_data_new<-full_data_new[!(full_data_new$stimulus_effect=="Image2-attended-never tested"),]
# full_data_new<-full_data_new[!(full_data_new$stimulus_effect=="Image1-attended-never tested"),]
# full_data_new<-full_data_new[!(full_data_new$stimulus_effect=="Image2-unattended-never tested"),]
# full_data_new<-full_data_new[!(full_data_new$stimulus_effect=="Image1-unattended-never tested"),]
# 
# 
# full_data$participant = as.factor(full_data$participant)
# 
# summary_ltm <-full_data %>%
#   group_by(task,exp_condition, participant) %>%
#   get_summary_stats(accuracy_t1, type = "mean_sd")
# 
# summary_ltm_new <-full_data_new %>%
#   group_by(task,exp_condition, participant,stimulus_effect) %>%
#   get_summary_stats(accuracy_t1, type = "mean_sd")
# 
# 
# 
# print("The following ANOVA displays the results of all trial conditions (excluding never tested trials) across the two tasks")
# 
# summary_ltm$exp_condition <- factor(summary_ltm$exp_condition)
# summary_ltm$task <- factor(summary_ltm$task)
# 
# summary_ltm <- summary_ltm %>%
#   mutate(exp_condition = recode(exp_condition, "Test 1" = "Test1", "Test 2" = "Test2"))
# 
# res.aov2_task <- anova_test(data = summary_ltm, dv = mean, wid = participant, within = c(exp_condition, task))
# 
# print("We see a sig. main effect of task, indicating better performance in WM task")
# get_anova_table(res.aov2_task)

```





